lord vorotron: finding the best JFA variant for the coming winter

### 2020-09-17 paper/main.tex
add new sections
small fix
fancy ACM style

\documentclass{article}

@@

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{float}

@@

%%% BONUS %%%
\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
\newcolumntype{L}{>{\raggedright\footnotesize}m{6cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

%%% BIBTEX %%%
% https://sunsite.icm.edu.pl/pub/CTAN/info/biblatex-cheatsheet/biblatex-cheatsheet.pdf
\usepackage[backend=bibtex, style=numeric, sorting=ynt]{biblatex}
\addbibresource{main.bib} %                       `ynt` vs. `ydnt`
\newcommand{\citep}[1]{\citeauthor*{#1} \cite{#1}} % for `fancy` cite style
%%%%%%%%%%%%%%

@@

\renewcommand{\headeright}{}
\renewcommand{\undertitle}{Draft}
\renewcommand{\shorttitle}{\ourjfa}

@@

\author{
  Maciej A.~Czyzewski\\
  Institute of Computing Science\\
  Poznan University of Technology\\
  Piotrowo 2, 60-965 Poznan, Poland\\
  \texttt{maciejanthonyczyzewski@gmail.com} \\
  \And
  Kamil~Piechowiak\\
  Institute of Computing Science\\
  Poznan University of Technology\\
  Piotrowo 2, 60-965 Poznan, Poland\\
  \texttt{kamil.cams@gmail.com} \\
}

@@

@@

@@

\begin{itemize}
	\item \textbf{shapes}: \{(64, 64), (128, 128), (256, 256), (512, 512), (768,
		768)\}
	\item \textbf{cases}:
        \begin{itemize}
			\item gen\_uniform: seeds=1,
			\item gen\_uniform: seeds=2,
			\item gen\_uniform: density=0.0001,
			\item gen\_uniform: density=0.001,
			\item gen\_uniform: density=0.01,
			\item gen\_uniform: density=0.02,
			\item gen\_uniform: density=0.03,
			\item gen\_uniform: density=0.04,
			\item gen\_uniform: density=0.05,
			\item gen\_uniform: density=0.1,
		\end{itemize}
\end{itemize}

@@

\subsection{Multi-domain Algorithm (JFAStar)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\hl{naprawic generowanie tego wykresu}

@@

\printbibliography

>>>>

\documentclass[format=acmsmall,screen,review,authordraft,nonacm]{acmart}
%\documentclass[format=acmsmall,screen,review,authordraft]{acmart}
%\documentclass{article}

% FIXME: https://arxiv.org/pdf/1709.06182.pdf
%        maja ladny template / chyba dziabne
%        albo ten z brytyjskiego sem6
%      https://github.com/borisveytsman/acmart

@@

%\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{float}

@@

%%% BONUS %%%
%\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{6cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

%%% BIBTEX %%%
% https://sunsite.icm.edu.pl/pub/CTAN/info/biblatex-cheatsheet/biblatex-cheatsheet.pdf
%\usepackage[backend=bibtex, style=numeric, sorting=ynt]{biblatex}
%\addbibresource{main.bib} %                       `ynt` vs. `ydnt`
%\newcommand{\citep}[1]{\citeauthor*{#1} \cite{#1}} % for `fancy` cite style
%%%%%%%%%%%%%%

@@

%\renewcommand{\headeright}{}
%\renewcommand{\undertitle}{Draft}
%\renewcommand{\shorttitle}{\ourjfa}

@@

\author{Maciej A. Czyzewski}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

\author{Kamil Piechowiak}
\affiliation{%
 \institution{Poznan University of Technology}
 \city{Poznan}
 \country{Poland}}

% \author{
%   Maciej A.~Czyzewski\\
%   Institute of Computing Science\\
%   Poznan University of Technology\\
%   Piotrowo 2, 60-965 Poznan, Poland\\
%   \texttt{maciejanthonyczyzewski@gmail.com} \\
%   \And
%   Kamil~Piechowiak\\
%   Institute of Computing Science\\
%   Poznan University of Technology\\
%   Piotrowo 2, 60-965 Poznan, Poland\\
%   \texttt{kamil.cams@gmail.com} \\
% }

@@

\url{https://arxiv.org/pdf/1801.09373.pdf}
\url{https://arxiv.org/pdf/1804.10120.pdf}
\url{https://arxiv.org/pdf/1703.06353.pdf}

@@

\hl{okay, zupelnie inaczej tutaj podejsc, opisac jakie sa przypadki i jakie sa
spotykane}

@@

@@

\subsection{Multi-domain Algorithm (JFAStar)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item \textbf{shapes}: \{32x32, 64x64, 96x96, 128x128, 256x256, 320x320, 384x384, 448x448, 512x512, 768x768, 1024x1024, 1536x1536\}
	\item \textbf{cases}:
        \begin{itemize}
			\item gen\_uniform: seeds=1,
			\item gen\_uniform: seeds=2,
			\item gen\_uniform: density=0.0001,
			\item gen\_uniform: density=0.001,
			\item gen\_uniform: density=0.01,
			\item gen\_uniform: density=0.02,
			\item gen\_uniform: density=0.03,
			\item gen\_uniform: density=0.04,
			\item gen\_uniform: density=0.05,
			\item gen\_uniform: density=0.1,
		\end{itemize}
\end{itemize}

@@

\subsection{Specific-domain Algorithm} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{32x32, 64x64, 96x96, 128x128}

\subsubsection{256x256, 320x320, 384x384, 448x448}

\subsubsection{512x512, 768x768, 1024x1024, 1536x1536}

\subsubsection{Low Density}

\subsubsection{High Density}

\subsection{Ensemble Across Domains (Vorotron)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

bla bla

@@

\hl{naprawic generowanie tego wykresu}
\hl{napisac co nie moze byc uzyte z czym?}

@@

%\printbibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{main}
